---
title: "p8105_hw1_zj2358"
author: "Zhezheng Jin"
date: "2023-09-17"
output: github_document
---

## Problem 1

# Load the dataset

```{r}
library(moderndive)
data("early_january_weather")
```

# View the dataset structure

```{r}
?early_january_weather
```

# Number of rows and columns in the dataset

```{r}
nrow(early_january_weather) 
ncol(early_january_weather) 
```

# Mean temperature

```{r}
mean(early_january_weather$temp)
```

# Description of dataset "early_january_weather"

The "early_january_weather" dataset contains hourly meteorological data for January 2013 from three weather stations (LGA, JFK, EWR) in the New York City area.This is a subset of the weather data frame from nycflights13. It includes 15 variables:
origin: Weather station.

year, month, day, hour: Time of recording.

temp, dewp: Temperature and dewpoint in F.

humid: Relative humidity.

wind_dir, wind_speed, wind_gust: Wind direction (in degrees), speed and gust speed (in mph).

precip: Precipitation, in inches.

pressure: Sea level pressure in millibars.

visib: Visibility in miles.

time_hour: Date and hour of the recording as a POSIXct date.

The dataset comprises 358 rows and 15 columns.

The mean temperature for the dataset is 39.58 F.

# Load the required libraries

```{r}
library(ggplot2)
```

# Create the scatterplot

```{r}
scatterplot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(
    x = "Time Hour",
    y = "Temperature (F)",
    color = "Humidity"
  ) +
  theme_minimal()
```

# Display the scatterplot

```{r}
scatterplot
```

# Describe patterns

There is a non-linear trend between Temperature and Time Hour. The temperature Range is from about 24 to 58 F. Clusters of points in the plot are concentrated in the range of 35-50 F. There's a consistent relationship between temperature and humidity. As humidity increases, temperatures tend to increase.

# Export to the project directory

```{r}
ggsave("scatterplot_temp_vs_time_hour.png", scatterplot, width = 10, height = 6)
```

## Problem 2

# Load the tidyverse package

```{r}
library(tidyverse)
```

# Set a random seed for reproducibility

```{r}
set.seed(123)
```

# Create the data frame

```{r}
zj_df <- data.frame(
  random_samp = rnorm(10),                
  logical_vector = rnorm(10) > 0,           
  character_vector = sample(letters, 10, replace = TRUE),  
  factor_vector = as.factor(sample(1:3, 10, replace = TRUE)) 
)
```

# Calculate the mean for each variable

```{r}
mean_random <- mean(pull(zj_df, random_samp))
mean_logical <- mean(pull(zj_df, logical_vector))
mean_character <- mean(pull(zj_df, character_vector))
mean_factor <- mean(pull(zj_df, factor_vector))
```

After calculation, the random sample, and logical vector have mean values, but the character vector and factor vector do not have.

# Convert logical, character, and factor variables to numeric

```{r}
zj_df$logical_vector_numeric <- as.numeric(zj_df$logical_vector)
zj_df$character_vector_numeric <- as.numeric(zj_df$character_vector)
zj_df$factor_vector_numeric <- as.numeric(zj_df$factor_vector)
```

# Calculate the mean value again

```{r}
mean_random <- mean(pull(zj_df, random_samp))
mean_logical <- mean(pull(zj_df, logical_vector_numeric))
mean_character <- mean(pull(zj_df, character_vector_numeric))
mean_factor <- mean(pull(zj_df, factor_vector_numeric))
```

After the recalculation, the factor vector has a mean value, but the mean value of the character vector is still unvailable. Because as.numeric will convert the levels of the factor to their internal integer representations.This conversion to numeric values doesn't  help explain what happens when trying to take the mean because the numeric values may not hold the same meaning as the original data.
